### 2018-08-30 ms/ms_probaweb.tex

There are multiple causes of spatial turnover of species co-occurrence. The
first and most-studied driver is the effect of variation in the abiotic
environment on species performance. Combined with specific responses in
demography, it generates variation among sites by selecting the locally
fittest species \citep{Leibold2004a}. Stochasticity plays an additional role,
either because colonization and extinction events \citep{Hanski1999} are
inherently unpredictable or because strong non-linear feedbacks in community
dynamics generate alternative transients and equilibria \citep{Chase2007,
Vellend2014}. Interaction themselves may impact co-distribution, as
hypothesized long ago by \citet{Diamond1975}. Analyses of community turnover
are usually performed with data represented in a table with rows corresponding
to sites (or measurements) and columns to species. Metrics of beta diversity
quantify the variance of this community data \citep{Legendre2005}. Traditional
approaches rely on measures of dissimilarity among communities, such as the
Jaccard or Bray–Curtis indices. More recent approaches decompose total
variation of the community data into species and site contributions to beta
diversity \citep{Legendre2013}, and further partition it into dissimilarity
due to changes in species richness and dissimilarity due to actual species
turnover \citep{Baselga2010}. Even though all of these methods compare whole
lists of species among sites or measurements, they remain fundamentally
"species-based", since they report variation within columns. None of them
explicitly considers variation of associations (i.e., of pairs or higher-order
motifs – \citealt{Stouffer2007}). Some previous studies have considered how
species distribution could be influenced by the joint effects of the abiotic
and biotic environment \citep{Stephens2009, GonzalezSalazar2013, Cazelles2015,
Ovaskainen2017}, here we inverse the problem and describe how the distribution
of biotic interactions is influenced by species distribution and the
environment.

@@

%-----------------
\begin{equation}
	\text{P}(X_{iy},X_{jy},L_{ijy}|E_y)
\end{equation}
%-----------------

@@

%-----------------
\begin{equation}
	P(X_{iy},X_{jy},L_{ijy}|E_y)=P(X_{iy},X_{jy}|E_y)P(L_{ijy}|X_{iy},X_{jy},E_y)
\end{equation}
%-----------------

The first term on the right-hand side of the equation is the probability of
observing the two species co-occurring at location $y$. It corresponds to the
Grinnellian dimension of the niche. The second term represents the probability
that an interaction occurs between species $i$ and $j$, given that they are
co-occurring. This predicate can be refined using information on trait
distribution and trait matching rules . For brevity, we have here avoided
specific references to traits and considered that the interactions are
provided in the data. But one could develop the model further to integrate
such traits, inspired by the framework developed by Gravel et al. 2016. They
proposed to represent the occurence of an interaction between species as a
joint probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j|E)$, where
$\mathbf{T}_i$ and $\mathbf{T}_j$ are trait vectors for species $i$ and $j$
respectively. In order to develop a trait-based representation of the spatial
variation of interactions, one may thereafter consider how these traits are
related to the environment and how they co-occur. Above, we referred to this
entity as the "metaweb" and note that it corresponds to the Eltonian dimension
of the niche. Below, we will see how this formalism can be directly fit to
empirical data, restricting ourselves to occurrences only and refering to the
above citations for trait-matching and trait-environment relationships. But
before turning to an application, we will discuss the interpretation of
different variants of these two terms.

@@

There are several variants to the co-occurrence probability, representing
different hypotheses concerning spatial variation in network structure (see
the explicit formulations in Table 1). The simplest model relates the
probability of co-occurrence directly to the environment,
$P(X_{iy},X_{jy}|E_y)$. In this situation, there are no underlying assumptions
about the ecological processes responsible for co-occurrence. Spatial associations between species could arise
because interactions constrain distribution, where in such case the co-occurrence would be conditional on $L$, or, alternatively, because of
environmental requirements shared between $i$ and $j$ \citep{Pollock2014,
Cazelles2016}. In the former case, species are not independent of each other
and the conditional occurrence must be accounted for explicitly,
$P(X_{iy},X_{jy} |E_y)=P(X_{iy}|E_y,X_{jy})P(X_{jy}|E_y)$. In the latter case,
species are independent, and only the marginal occurrence must be accounted
for, $P( X_{ijy}|E_y)=P(X_{iy} |E_y)P(X_{jy} |E_y)$.

@@

There are also variants of the metaweb. First, most documented metawebs have
thus far considered ecological interactions to be deterministic, rather than
probabilistic (e.g. \citealt{Havens1992, Wood2015}). Species are assumed to
interact whenever they are found together in a location, independent of their
local abundance and the local environment. In other words,
$P(L_{ijy}|X_{iy}=1,X_{jy}=1) = 1$. This approach might be a reasonable
approximation if the spatial or temporal scale of sampling and inference is so
large that the probability of observing at least one interaction converges to
unity. In this scenario, network variation arises solely from species
distributions.

Second, ecological interactions could also vary with the environment, so that
$P(L_{ijy}|E_y)$. Although it is rare to see a conditional representation of
pairwise ecological interactions, experimental studies have frequently
revealed interactions to be sensitive to the environment. For instance,
\citet{Mckinnon2010} showed that predation risks of shorebirds vary at the
continental scale, decreasing from the south to the north. It is also common
to see increasing top-down control with temperature (e.g. \citealt{Shurin2012,
Gray2016}). Effects of the environment on interactions \citep{Gibert2014} also
propagate up the community and influence network structure
\citep{Tylianakis2007, Woodward2010, Petchey2010a}.

@@

We compared three models for the co-occurrence probability. The first one
directly represents the co-occurrence probability conditional on the local
environment, $P(X_{iy},X_{jy}|E_y)$ (models are listed in Tables 1 and 2).
Hence, this model makes no assumption about the mechanisms driving co-
occurrence for any given environment, and instead uses the information
directly available in the data. It thereby indirectly accounts for the effect
of interactions on co-occurrence, if there are any. The second model considers
independent occurrence of species. In this case, we independently fit
$P(X_{iy} |E_y)$ and $P(X_{jy} |E_y)$, and we then take their product to
derive the probability of co-occurrence. This model should be viewed as a null
hypothesis with respect to the first model, since a comparison between the
respective models will reveal if there is significant spatial association of
the two species beyond a joint response to the shared environment
\citep{Cazelles2016}. Finally, the third model assumes that the probability of
co-occurrence is independent of the environment and thus constant throughout
the landscape. In other words, $P(X_{iy},X_{jy})$ is obtained by simply
counting the number of observed co-occurrences divided by the total number of
observations. Thus, the comparison between the first and third model allows us
to test the hypothesis that co-occurrence is conditional on the environment.
Whenever the environment was included as a covariate in the GLM, we considered
a second-order polynomial term for both temperature and precipitation in
order to account for optima in environmental conditions. There are
consequently five parameters for the first model when fitting a given pair of
species, 10 parameters for the second, and only one for the third model.

Following the same logic, we compared three models of the interaction
probability. The first model conditions the interaction probability on the
local environmental variables, $P(L_{ijy}|X_{iy},X_{jy},E_y)$. Consequently,
the model was fit to the subset of the data where the two species co-occur.
The second model fits the interaction probability independently of the local
environmental variables, $P(L_{ijy}|X_{iy},X_{jy})$. It corresponds to the
number of times the two species were observed to interact when co-occurring,
divided by the number of times that they co-occurred. The third model is an
extreme case evaluated only to test the hypothesis that if two species are
found to interact at least once, then they should interact whenever they co-occur, $P(L_{ijy}|X_{iy},X_{jy})=1$. While not necessarily realistic, this
model tests an assumption commonly invoked in the representation of local
networks from the knowledge of a deterministic metaweb. It represents
potential interactions, rather than realized ones. There are consequently five
parameters for the first model, a single parameter for the second model and no
parameter to evaluate for the third model (where the interaction probability
is fixed by the hypothesis).

We fitted the different models to each pair of species and recorded the
predicted probabilities. The joint probability $P(L_{ijy},X_{iy},X_{jy})$ was
then computed from Eq. 2, and the likelihood of each observation $D_{ijy}$ given the model $\theta$ was computed
as $\mathcal{L}(D_{ijy}|\theta)=P(L_{ij},X_{iy},X_{jy})$ if an
interaction was observed, and as $\mathcal{L}(D_{ijy}|\theta) =
1-P(L_{ijy}, X_{iy}, X_{jy})$ if no interaction was observed. The log-likelihood was summed over the entire dataset to compare the different models
by AIC. We therefore evaluate the likelihood of all local networks, given the
model. Not surprisingly, there was a very large number of species pairs for
which this model could not be computed, as they simply never co-occurred. For
these pairs, we have no information of the interaction probability, and they
were consequently removed from the analysis. The log-likelihood reported
across the entire dataset was therefore summed over all pairs of species observed to co-occur at least once. Interactions between the first (\textit{Salix}) and
second (gallers) trophic layers and those between the second and third
(parasitoids) were considered separately. Finally, we used the full model (in
which both co-occurrence and the interaction are conditional on the
environment) to interpolate species distributions and interaction
probabilities across the entire European continent. We reconstructed the
expected network for each location in a 1 X 1 km grid and computed the
probabilistic connectance following \citet{Poisot2015c}.

@@

The framework we provide complements methods to compute network beta-diversity
presented by \citealt{Poisot2012} and \citealt{Poisot2018}. The total network
turnover is partitioned into interaction turnover and species turnover – which
in our approach would correspond to the three terms of Eq. 2, respectively.
Importantly, one could easily derive the different $\beta$ of
\citealt{Poisot2012} using the fitted probabilities. For instance, for a pair
of species $i$ and $j$ and sites $x$ and $y$, the expectation for the fraction
$a$ for the interactions would be
$P(L_{ijx}|X_{ix},X_{ijx})P(L_{ijx}|X_{ix},X_{ijx})$. The same could be
computed for fractions $b$, and therefore the expected beta-diversity for an
entire network could be recomputed this way. The novel feature of the approach
presented here is then that the different contributions to network turnover
can be attributed to different hypotheses (as performed here), in order to
evaluate for instance the role of environmental heterogeneity or species co-
distribution on network turnover.

We restricted our analysis to the effect of co-occurrence on ecological
interactions, neglecting the inverse of the problem. We did not investigate in
depth the drivers of co-occurrence and simply took it for granted from the
data. Co-occurrence was indeed different from the expectation of independent
species distributions. It thus begs the question of whether, once
environmental effects on species-specific distribution have been accounted
for, interactions come with significant effects on co-occurrence? We could
rephrase this problem by asking whether the fundamental niche differs from the
realized niche, and how this applies to our framework. For example, we have
considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}|E_y)$,
which could be expanded as $P(X_{iy}|X_{jy},E_y) P(X_{jy}| E_y )$. After some
re-arrangement of Eq. 2, the marginal occurrence probability, $P(X_{jy}|E_y
)$, could be considered as a species distribution model taking into account
the interaction between these species (in the same spirit as done by Gonzalez-
Salazar et al. 2013). This derivation would however critically depend on a
strong \emph{a priori} expectation of the conditional probability of observing
a species given the distribution of the other species. This assumption seems
reasonable for some situations, such as a parasitoid species that requires a
host to develop. On the other hand, \citet{Cazelles2016b} found that the
strength of this association is often rather weak if not inexistant (for
instance, with the example pair presented in Table 1). The lack of an
association could simply arise when the parasitoid is generalist enough that
it is not constrained to track the distribution of any single/given host
\citep{Cazelles2015}.

The approach we presented could easily be expanded to account for traits, in
order to derive a complete and more mechanistic representation of the niche.
In this context, both the Eltonian and Grinnellian dimensions of the niche
could be represented. As mentioned earlier, \citealt{Gravel2016} proposed to
represent the occurrence of interactions based on some trait-matching rules
(given by a function of the type $P(L_{ij})|\mathbf{T}_i, \mathbf{T}_j, E)$)
and the co-distribution of traits (corresponding to $P(\mathbf{T}_i,
\mathbf{T}_j|E)$). The key  insight from the formalism proposed by
\citealt{Gravel2016} is that the co-distribution of traits will impact
variation in network structure. As a result, it was found that network
properties often co-vary with functional structure and functional diversity
\citealp{Laigle2018}. The next step in the development of this framework will
be to develop the models for the co-distribution of traits, for instance
following Ovaskainen et al. 2017. This may facilitate the accessibility and
the applicability of the framework, since the basic unit of analysis is no
longer the species, but rather a combination of traits, thereby facilitating
the statistical analysis by sharing information among species.

@@

\begin{tabular}{llllllll}
\hline
Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Av. temp \\ \hline
Kühkopf 		& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 1 &  8.25 \\
Kühkopf 		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  8.25 \\
Ötztal 			& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
Ötztal 			& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
Kilpisjärvi		& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
Kilpisjärvi		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
Wüstensachsen	& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 0 &  5.58 \\
Wüstensachsen	& Phyllocolpa leucapsis & Chrysocharis elongata & 1 & 1 & 1 & 1 &  5.58 \\
Steinamoen      & Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\
Steinamoen      & Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\ 
\hline
\end{tabular}
\end{table}
%\end{landscape}

\newpage
%========================================================%
\begin{landscape}
\begin{table}[]
\centering
\caption{Summary of model comparison for the interaction between the leaf
folder \textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
elongata}}. Note that $E$ is a short notation including both temperature and precipitation.
\begin{tabular}{llllll}
\hline
	\# & Metaweb model 						& Co-occurrence model 			& LL 	& npars & AIC \\ \hline
	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}|E_y)$ 		& -71.1 & 6 	& 154.2 \\
	2 & $P(L_{ijy} | X_{iy}, X_{jy})$ 		& $P(X_{iy},X_{jy}|E_y)$ 		& -65.7 & 6 	& 143.4 \\
	3 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}|E_y)$ 		& -65.6 & 10 	& 151.3 \\ \hline
	4 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ 			& -84.5 & 6 	& 183 \\
	5 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ 			& -80.7 & 7 	& 173.4 \\
	6 & $P(L_{ijy} | X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}|E_y)P(X_{jy}|E_y)$ 	& -68.8 & 15 	& 167.6 \\
\hline
\end{tabular}
\end{table}
\end{landscape}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=1\textwidth]{figures/mw_sampling}
\end{figure}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=0.6\textwidth]{figures/integrated_niche}
\end{figure}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/example_pair}
\end{figure}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/map_pair}
\end{figure}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/map_connectance}
\end{figure}

>>>>

There are multiple causes of spatial turnover of species co-occurrence. The
first and most-studied driver is the effect of variation in the abiotic
environment on species performance. Combined with specific responses in
demography, it generates variation among sites by selecting the locally
fittest species \citep{Leibold2004a}. Stochasticity plays an additional role,
either because colonization and extinction events \citep{Hanski1999} are
inherently unpredictable or because strong non-linear feedbacks in community
dynamics generate alternative transients and equilibria \citep{Chase2007,
Vellend2014}. Interaction themselves may impact co-distribution, as
hypothesized long ago by \citet{Diamond1975}. Analyses of community turnover
are usually performed with data represented in a table with rows corresponding
to sites (or measurements) and columns to species. Metrics of beta diversity
quantify the variance of this community data \citep{Legendre2005}. Traditional
approaches rely on measures of dissimilarity among communities, such as the
Jaccard or Bray–Curtis indices. More recent approaches decompose total
variation of the community data into species and site contributions to beta
diversity \citep{Legendre2013}, and further partition it into dissimilarity
due to changes in species richness and dissimilarity due to actual species
turnover \citep{Baselga2010}. Even though all of these methods compare whole
lists of species among sites or measurements, they remain fundamentally
"species-based", since they report variation within columns. None of them
explicitly considers variation of associations (i.e., of pairs or higher-order
motifs – \citealt{Stouffer2007}). Some previous studies have considered how
species distribution could be influenced by the joint effects of the abiotic
and biotic environment \citep{Stephens2009, GonzalezSalasar2013, Cazelles2015,
Ovaskainen2017}, here we inverse the problem and describe how the distribution
of biotic interactions is influenced by species distribution and the
environment.

@@

%-----------------
\begin{equation}
	\text{P}(X_{iy},X_{jy},L_{ijy}\lvert E_y)
\end{equation}
%-----------------

@@

%-----------------
\begin{equation}
	P(X_{iy},X_{jy},L_{ijy}\lvert E_y)=P(X_{iy},X_{jy}\lvert E_y)P(L_{ijy}\lvert X_{iy},X_{jy},E_y)
\end{equation}
%-----------------

The first term on the right-hand side of the equation is the probability of
observing the two species co-occurring at location $y$. It corresponds to the
Grinnellian dimension of the niche. The second term represents the probability
that an interaction occurs between species $i$ and $j$, given that they are
co-occurring. This predicate can be refined using information on trait
distribution and trait matching rules . For brevity, we have here avoided
specific references to traits and considered that the interactions are
provided in the data. But one could develop the model further to integrate
such traits, inspired by the framework developed by Gravel et al. 2016. They
proposed to represent the occurence of an interaction between species as a
joint probability event $P(L_{ij}, \mathbf{T}_i, \mathbf{T}_j\lvert E)$, where
$\mathbf{T}_i$ and $\mathbf{T}_j$ are trait vectors for species $i$ and $j$
respectively. In order to develop a trait-based representation of the spatial
variation of interactions, one may thereafter consider how these traits are
related to the environment and how they co-occur. Above, we referred to this
entity as the "metaweb" and note that it corresponds to the Eltonian dimension
of the niche. Below, we will see how this formalism can be directly fit to
empirical data, restricting ourselves to occurrences only and refering to the
above citations for trait-matching and trait-environment relationships. But
before turning to an application, we will discuss the interpretation of
different variants of these two terms.

@@

There are several variants to the co-occurrence probability, representing
different hypotheses concerning spatial variation in network structure (see
the explicit formulations in Table 1). The simplest model relates the
probability of co-occurrence directly to the environment,
$P(X_{iy},X_{jy}\lvert E_y)$. In this situation, there are no underlying assumptions
about the ecological processes responsible for co-occurrence. Spatial associations between species could arise
because interactions constrain distribution, where in such case the co-occurrence would be conditional on $L$, or, alternatively, because of
environmental requirements shared between $i$ and $j$ \citep{Pollock2014,
Cazelles2016}. In the former case, species are not independent of each other
and the conditional occurrence must be accounted for explicitly,
$P(X_{iy},X_{jy} \lvert E_y)=P(X_{iy}\lvert E_y,X_{jy})P(X_{jy}\lvert E_y)$. In the latter case,
species are independent, and only the marginal occurrence must be accounted
for, $P( X_{ijy}\lvert E_y)=P(X_{iy} \lvert E_y)P(X_{jy} \lvert E_y)$.

@@

There are also variants of the metaweb. First, most documented metawebs have
thus far considered ecological interactions to be deterministic, rather than
probabilistic (e.g. \citealt{Havens1992, Wood2015}). Species are assumed to
interact whenever they are found together in a location, independent of their
local abundance and the local environment. In other words,
$P(L_{ijy}\lvert X_{iy}=1,X_{jy}=1) = 1$. This approach might be a reasonable
approximation if the spatial or temporal scale of sampling and inference is so
large that the probability of observing at least one interaction converges to
unity. In this scenario, network variation arises solely from species
distributions.

Second, ecological interactions could also vary with the environment, so that
$P(L_{ijy}\lvert E_y)$. Although it is rare to see a conditional representation of
pairwise ecological interactions, experimental studies have frequently
revealed interactions to be sensitive to the environment. For instance,
\citet{Mckinnon2010} showed that predation risks of shorebirds vary at the
continental scale, decreasing from the south to the north. It is also common
to see increasing top-down control with temperature (e.g. \citealt{Shurin2012,
Gray2016}). Effects of the environment on interactions \citep{Gibert2014} also
propagate up the community and influence network structure
\citep{Tylianakis2007, Woodward2010, Petchey2010a}.

@@

We compared three models for the co-occurrence probability. The first one
directly represents the co-occurrence probability conditional on the local
environment, $P(X_{iy},X_{jy}\lvert E_y)$ (models are listed in Tables 1 and 2).
Hence, this model makes no assumption about the mechanisms driving co-
occurrence for any given environment, and instead uses the information
directly available in the data. It thereby indirectly accounts for the effect
of interactions on co-occurrence, if there are any. The second model considers
independent occurrence of species. In this case, we independently fit
$P(X_{iy} \lvert E_y)$ and $P(X_{jy} \lvert E_y)$, and we then take their product to
derive the probability of co-occurrence. This model should be viewed as a null
hypothesis with respect to the first model, since a comparison between the
respective models will reveal if there is significant spatial association of
the two species beyond a joint response to the shared environment
\citep{Cazelles2016}. Finally, the third model assumes that the probability of
co-occurrence is independent of the environment and thus constant throughout
the landscape. In other words, $P(X_{iy},X_{jy})$ is obtained by simply
counting the number of observed co-occurrences divided by the total number of
observations. Thus, the comparison between the first and third model allows us
to test the hypothesis that co-occurrence is conditional on the environment.
Whenever the environment was included as a covariate in the GLM, we considered
a second-order polynomial term for both temperature and precipitation in
order to account for optima in environmental conditions. There are
consequently five parameters for the first model when fitting a given pair of
species, 10 parameters for the second, and only one for the third model.

Following the same logic, we compared three models of the interaction
probability. The first model conditions the interaction probability on the
local environmental variables, $P(L_{ijy}\lvert X_{iy},X_{jy},E_y)$. Consequently,
the model was fit to the subset of the data where the two species co-occur.
The second model fits the interaction probability independently of the local
environmental variables, $P(L_{ijy}\lvert X_{iy},X_{jy})$. It corresponds to the
number of times the two species were observed to interact when co-occurring,
divided by the number of times that they co-occurred. The third model is an
extreme case evaluated only to test the hypothesis that if two species are
found to interact at least once, then they should interact whenever they co-occur, $P(L_{ijy}\lvert X_{iy},X_{jy})=1$. While not necessarily realistic, this
model tests an assumption commonly invoked in the representation of local
networks from the knowledge of a deterministic metaweb. It represents
potential interactions, rather than realized ones. There are consequently five
parameters for the first model, a single parameter for the second model and no
parameter to evaluate for the third model (where the interaction probability
is fixed by the hypothesis).

We fitted the different models to each pair of species and recorded the
predicted probabilities. The joint probability $P(L_{ijy},X_{iy},X_{jy})$ was
then computed from Eq. 2, and the likelihood of each observation $D_{ijy}$ given the model $\theta$ was computed
as $\mathcal{L}(D_{ijy}\lvert \theta)=P(L_{ij},X_{iy},X_{jy})$ if an
interaction was observed, and as $\mathcal{L}(D_{ijy}\lvert \theta) =
1-P(L_{ijy}, X_{iy}, X_{jy})$ if no interaction was observed. The log-likelihood was summed over the entire dataset to compare the different models
by AIC. We therefore evaluate the likelihood of all local networks, given the
model. Not surprisingly, there was a very large number of species pairs for
which this model could not be computed, as they simply never co-occurred. For
these pairs, we have no information of the interaction probability, and they
were consequently removed from the analysis. The log-likelihood reported
across the entire dataset was therefore summed over all pairs of species observed to co-occur at least once. Interactions between the first (\textit{Salix}) and
second (gallers) trophic layers and those between the second and third
(parasitoids) were considered separately. Finally, we used the full model (in
which both co-occurrence and the interaction are conditional on the
environment) to interpolate species distributions and interaction
probabilities across the entire European continent. We reconstructed the
expected network for each location in a 1 X 1 km grid and computed the
probabilistic connectance following \citet{Poisot2015c}.

@@

The framework we provide complements methods to compute network beta-diversity
presented by \citealt{Poisot2012} and \citealt{Poisot2018}. The total network
turnover is partitioned into interaction turnover and species turnover – which
in our approach would correspond to the three terms of Eq. 2, respectively.
Importantly, one could easily derive the different $\beta$ of
\citealt{Poisot2012} using the fitted probabilities. For instance, for a pair
of species $i$ and $j$ and sites $x$ and $y$, the expectation for the fraction
$a$ for the interactions would be
$P(L_{ijx}\lvert X_{ix},X_{ijx})P(L_{ijx}\lvert X_{ix},X_{ijx})$. The same could be
computed for fractions $b$, and therefore the expected beta-diversity for an
entire network could be recomputed this way. The novel feature of the approach
presented here is then that the different contributions to network turnover
can be attributed to different hypotheses (as performed here), in order to
evaluate for instance the role of environmental heterogeneity or species co-
distribution on network turnover.

We restricted our analysis to the effect of co-occurrence on ecological
interactions, neglecting the inverse of the problem. We did not investigate in
depth the drivers of co-occurrence and simply took it for granted from the
data. Co-occurrence was indeed different from the expectation of independent
species distributions. It thus begs the question of whether, once
environmental effects on species-specific distribution have been accounted
for, interactions come with significant effects on co-occurrence? We could
rephrase this problem by asking whether the fundamental niche differs from the
realized niche, and how this applies to our framework. For example, we have
considered above simply the co-occurrence probability, $P(X_{iy},X_{jy}\lvert E_y)$,
which could be expanded as $P(X_{iy}\lvert X_{jy},E_y) P(X_{jy}\lvert  E_y )$. After some
re-arrangement of Eq. 2, the marginal occurrence probability, $P(X_{jy}\lvert E_y
)$, could be considered as a species distribution model taking into account
the interaction between these species (in the same spirit as done by Gonzalez-
Salazar et al. 2013). This derivation would however critically depend on a
strong \emph{a priori} expectation of the conditional probability of observing
a species given the distribution of the other species. This assumption seems
reasonable for some situations, such as a parasitoid species that requires a
host to develop. On the other hand, \citet{Cazelles2016b} found that the
strength of this association is often rather weak if not inexistant (for
instance, with the example pair presented in Table 1). The lack of an
association could simply arise when the parasitoid is generalist enough that
it is not constrained to track the distribution of any single/given host
\citep{Cazelles2015}.

The approach we presented could easily be expanded to account for traits, in
order to derive a complete and more mechanistic representation of the niche.
In this context, both the Eltonian and Grinnellian dimensions of the niche
could be represented. As mentioned earlier, \citealt{Gravel2016} proposed to
represent the occurrence of interactions based on some trait-matching rules
(given by a function of the type $P(L_{ij})\lvert \mathbf{T}_i, \mathbf{T}_j, E)$)
and the co-distribution of traits (corresponding to $P(\mathbf{T}_i,
\mathbf{T}_j\lvert E)$). The key  insight from the formalism proposed by
\citealt{Gravel2016} is that the co-distribution of traits will impact
variation in network structure. As a result, it was found that network
properties often co-vary with functional structure and functional diversity
\citealp{Laigle2018}. The next step in the development of this framework will
be to develop the models for the co-distribution of traits, for instance
following Ovaskainen et al. 2017. This may facilitate the accessibility and
the applicability of the framework, since the basic unit of analysis is no
longer the species, but rather a combination of traits, thereby facilitating
the statistical analysis by sharing information among species.

@@

\begin{tabular}{llllllll}
\hline

Location & $Sp_i$ & $Sp_j$ & $X_i$ & $X_j$ & $X_{ij}$ & $L_{ij}$ & Av. temp \\ \hline
Kühkopf 		& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 1 &  8.25 \\
Kühkopf 		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  8.25 \\
Ötztal 			& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
Ötztal 			& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 0 & 0 & 0 & -1.50 \\
Kilpisjärvi		& Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
Kilpisjärvi		& Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 & -1.92 \\
Wüstensachsen	& Phyllocolpa prussica  & Chrysocharis elongata & 1 & 1 & 1 & 0 &  5.58 \\
Wüstensachsen	& Phyllocolpa leucapsis & Chrysocharis elongata & 1 & 1 & 1 & 1 &  5.58 \\
Steinamoen      & Phyllocolpa prussica  & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\
Steinamoen      & Phyllocolpa leucapsis & Chrysocharis elongata & 0 & 1 & 0 & 0 &  3.17 \\

\hline
\end{tabular}
\end{table}
%\end{landscape}

\newpage
%========================================================%
\begin{landscape}
\begin{table}[]
\centering
\caption{Summary of model comparison for the interaction between the leaf
folder \textit{Phyllocolpa prussica}) and the parasitoid \textit{Chrysocharis
elongata}}. Note that $E$ is a short notation including both temperature and precipitation.
\begin{tabular}{llllll}
\hline
	\# & Metaweb model 						& Co-occurrence model 			& LL 	& npars & AIC \\ \hline
	1 & $P(L_{ijy})$ 						& $P(X_{iy},X_{jy}\lvert E_y)$ 		& -71.1 & 6 	& 154.2 \\
	2 & $P(L_{ijy} \lvert  X_{iy}, X_{jy})$ 		& $P(X_{iy},X_{jy}\lvert E_y)$ 		& -65.7 & 6 	& 143.4 \\
	3 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy}\lvert E_y)$ 		& -65.6 & 10 	& 151.3 \\ \hline
	4 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy},X_{jy})$ 			& -84.5 & 6 	& 183 \\
	5 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy})P(X_{jy})$ 			& -80.7 & 7 	& 173.4 \\
	6 & $P(L_{ijy} \lvert  X_{iy}, X_{jy}, E_y)$ & $P(X_{iy}\lvert E_y)P(X_{jy}\lvert E_y)$ 	& -68.8 & 15 	& 167.6 \\
\hline
\end{tabular}
\end{table}
\end{landscape}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=1\textwidth]{figures/mw_sampling.png}
\end{figure}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=0.6\textwidth]{figures/integrated_niche.png}
\end{figure}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/example_pair.png}
\end{figure}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/map_pair.png}
\end{figure}

@@

\begin{figure}[ht!]
\centering\includegraphics[width=0.8\textwidth]{figures/map_connectance.png}
\end{figure}
